\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-06-26 thesis/novelty-intro.tex
Changed section on constant P(novel)

It is questionable whether this assumption holds in realistic scenarios.
\textbf{[Read the section from here on.]}
and for that a sampling scheme able to comply with it is now presented as well an unbiased sampling
scheme. A method to generate samples that match this \emph{criterium} of having a constant $P(novel)$ can be:

@@

According to this sampling algorithm, given any structure the probability of
variable $a$ being novel is constant. This is somehow unexpected as it means
the sampling method is biased to adjust the real distribution $G$ such that
exactly a constant percentage of drawn samples are novel.

Alternative, the sampling method described below is considered more correct as
it introduces no bias on the distribution $G$ describing the real distribution
and classes of $a$:
\begin{algorithm}[Draw samples with equal $P(novel)$]
\begin{enumerate}
\item Sample a graph structure $G$ (where variable $a$ can be any of the known or unknown classes)
\item Sample variables $x$ according to distribution $P_G(x)$.
\end{enumerate}
\end{algorithm}

Due to the highly bias needed to drawn a constant amount of novel sampes from any structure, the
author defends this assumption to be very strong and points that future work should avoid.

>>>>

It is questionable whether this assumption holds in realistic scenarios.
Note that in order to match this \emph{criterium} of having a constant $P(novel)$ samples needs to be
drawn with a method like:

@@

Alternative, it is expected that in a realistic scenario, samples are drawn with the following
unbiased method:
\begin{algorithm}[Draw samples with equal $P(novel)$]
\begin{enumerate}
\item Sample a graph structure $G$ (where variable $a$ can be any of the known or unknown classes)
\item Sample variables $x$ according to distribution $P_G(x)$.
\end{enumerate}
\end{algorithm}

If in reality samples are drawn according to this unbiased method, assuming a constant $P(novel)$
will negatively impact the exactness of the detector. For that reason the author defends this assumption
to be very strong and points that future work should try to develop methods to include structure information
on the probabilistic model to allow the system to deal with certain structures being more prone to produce
novel samples.
